An Algorithm to Prune Integer Overflow Tests

### 2012-08-10 doc/Manuscript/CGO/paper.tex
Added some more text in the paper.

% Why there is still the need to devise efficient methods to eliminate them.
A considerable amount of work has been done in the dynamic detection of
integer overflows~\cite{TODO}.
This approach consists in instrumenting the program in such a way that the
transformed binary is overflow aware.
Thus, if an overflow happens, then the instrumented program can take some
action, such as logging that event, or terminating the program.
There has been also some work aiming at reducing the instrumentation overhead
via static analysis~\cite{TODO}.
However, many authors, such as XX {\em et al.}~\cite[p.xx]{TODO} and
XX {\em et al.}~\cite[p.x]{TODO}, leave instrumentation pruning as future
work.
The goal of this paper is to bring this future back to the present.

@@

@@

>>>>

% Why there is still the need to devise efficient methods to eliminate them.
There exist recent research about the dynamic detection of
integer overflows~\cite{Brumley07,Dietz12}.
This approach consists in instrumenting the program in such a way that the
transformed binary is overflow aware.
Thus, if an overflow happens, then the instrumented program can take some
action, such as logging that event, or terminating the program.
There has been also some work aiming at reducing the instrumentation overhead
via static analysis~\cite{Molnar09,Zhang09}.
However, many authors, such as XX {\em et al.}~\cite[p.xx]{TODO} and
XX {\em et al.}~\cite[p.x]{TODO}, leave instrumentation pruning as future
work.
The goal of this paper is to bring this future back to the present.

@@

\noindent
\textbf{Propagating Ranges in Topological Order. }
After building the constraint graph, we find its strongly connected components.
We collapse these components in super nodes, and then proceed to propagate
ranges along the resulting digraph.
This approach is essential for scalability, because all the complexity of our
algorithm lies in the resolution of strong components.
As we have showed elsewhere~\cite{Victor12}, the vast majority of the strongly
connected components are singletons.
For instance, 99.11\% of the SCCs in SPEC CPU 2006 gcc (\texttt{403.gcc}) have
only one node.
Moreover, the composite components usually contain a small number of nodes.
As an example, the largest component in \texttt{403.gcc}, has 2,131 nodes,
even though gcc's constraint graph has over one million nodes.
This large SCC exists due to a long chain of mutually recursive function calls.

@@

Zhang {\em et al.}~\cite{Zhang09} have designed a static analysis to sanitize
programs against integer overflow based vulnerabilities.
They instrument integer operations in paths from a source to a sink.
In Zhang {\em et al.}'s context, sources are functions that read values from
users, and sinks are memory allocation operations.
Thus, contrary to our work, Zhang {\em et al.}'s only need to instrument
about 10\% of the integer operations in the program.
However, they do not use any form of range analysis to limit the number of
checks inserted in the transformed code.
